### 2022-04-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@0164ce425d534ca57568c97d08a18db32ffcf41c 🚀

We downloaded the data on bats hosts of betacoronaviruses assembled by
Becker et al. (2022) from
\texttt{https://www.viralemergence.org/betacov} on Aug.~2021, and
filtered it to ``known'' hosts (established before the emergence of
SARS-CoV-2) and ``novel'' hosts (confirmed through sampling since the
emergence of SARS-CoV-2). This database was assembled by a combination
of data mining and literature surveys.

@@

We downloaded the rangemap of every extant bat species that was either
classified as an empirically documented or a suspected host of
beta-coronaviruses (Becker et al.~2020), according to recent IUCN data
(IUCN 2021). The range maps were subsequently rasterized at a resolution
of approximately TK TP. For every pixel in the resulting raster where at
least one bat host of betacoronavirus was present, we extract the
species pool, which was used to calculate the following risk assessment
components: phylogenetic diversity, bat compositional uniqueness, and
predicted viral sharing risk.

@@

For every pixel, we measured Faith's Phylogenetic Diversity (Faith 1992)
based on a recent synthetic tree with robust time calibration, covering
about 6000 mammalian species (Upham et al.~2019). Faith's PD measures
the sum of unique branches from an arbitrary root to a set of tips, and
comparatively larger values indicate a more phylogenetic diverse species
pool. We measured phylogenetic diversity starting from the root of the
entire tree (and not from Chiroptera); this bears no consequences on the
resulting values, since all branches leading up to Chiroptera are only
counted one per species pool, and (as we explain when describing the
assembly of the composite risk map), all individual risk components are
ranged in {[}0,1{]}. This measure incorporates a richness component,
which we chose not to correct for; the interpretation of the
phylogenetic diversity is therefore a weighted species richness, that
accounts for phylogenetic over/under-dispersal in some places.

@@

@@

@@

@@

>>>>

We downloaded the data on bats hosts of betacoronaviruses assembled by
Becker et al. (2022) from
\texttt{https://www.viralemergence.org/betacov} on Apr.~2022, and
filtered it to ``known'' hosts (established before the emergence of
SARS-CoV-2) and ``novel'' hosts (confirmed through sampling since the
emergence of SARS-CoV-2). The original database was assembled by a
combination of data mining and literature surveys, including automated
alerts on the ``bats'' and ``coronavirus'' keywords to identify novel
empirical evidence of bats-betacoronaviruses associations.

@@

We downloaded the rangemap of every extant bat species that was either
classified as an empirically documented host of beta-coronaviruses from
the previous step, according to recent IUCN data (IUCN 2021). The range
maps were subsequently rasterized using the \texttt{rasterize} function
from \texttt{GDAL} (Rouault et al. 2022) at a resolution of
approximately \textbf{TK TP}. For every pixel in the resulting raster
where at least one bat host of betacoronavirus was present, we extract
the species pool (list of all bat species), which was used to calculate
the following risk assessment components: phylogenetic diversity, bat
compositional uniqueness, and predicted viral sharing risk.

@@

For every pixel, we measured Faith's Phylogenetic Diversity (Faith 1992)
based on a recent synthetic tree with robust time calibration, covering
about 6000 mammalian species (Upham et al. 2019). Faith's PD measures
the sum of unique branches from an arbitrary root to a set of tips, and
comparatively larger values indicate a more phylogenetic diverse species
pool. We measured phylogenetic diversity starting from the root of the
entire tree (and not from Chiroptera); this bears no consequences on the
resulting values, since all branches leading up to Chiroptera are only
counted one per species pool, and (as we explain when describing the
assembly of the composite risk map), all individual risk components are
ranged in {[}0,1{]}. This measure incorporates a richness component,
which we chose not to correct for; the interpretation of the
phylogenetic diversity is therefore a weighted species richness, that
accounts for phylogenetic over/under-dispersal in some places.

@@

\leavevmode\hypertarget{ref-Faith1992ConEva}{}%
Faith, D. P. 1992. Conservation evaluation and phylogenetic diversity. -
Biological Conservation 61: 1--10.

@@

\leavevmode\hypertarget{ref-IUCN2021IucRed}{}%
IUCN 2021. The IUCN Red List of Threatened Species.

@@

\leavevmode\hypertarget{ref-RouaultEven2022GdaOgr}{}%
Rouault, E. et al. 2022. GDAL/OGR Geospatial Data Abstraction software
Library. - Zenodo.

@@

\leavevmode\hypertarget{ref-Upham2019InfMam}{}%
Upham, N. S. et al. 2019. Inferring the mammal tree: Species-level sets
of phylogenies for questions in ecology, evolution, and conservation. -
PLOS Biology 17: e3000494.
